AUTOMATED TRANSCRIPTION OF DRUMSOUNDS

### 2017-08-15 Latex/Paper/main.tex
Ground structure of the paper

% Template for ICASSP-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}

@@

>>>>

% Template for ICASSP-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{blindtext}

@@

context, problem, use cases
definitions
paper overview

% section intro (end)

\section{Related work}
\label{sec:rel}

literature review, state of the art

% section rel (end)

\section{algorithm overview and description}
\label{sec:algo}

\blindtext

% section algo (end)

\section{Evaluation}
\label{sec:evaluation}

ground truth, methodology, metrics
results
discussion

% section evaluation (end)

\section{Conclusion}
\label{sec:conclusion}

summary, noteworthy parts of the presented work,
achievements and contributions
possible improvements and future work

% section conclusion (end)

%\end{document}

% DELETE EVERYTHING FROM HERE IN THE END
% DELETE EVERYTHING FROM HERE IN THE END
% DELETE EVERYTHING FROM HERE IN THE END

\section{common flaws}
all cited papers should appear in bibliography
vice versa: all references should be mentioned in the paper
each reference should contain:
names of authors
title of the paper or book
conference paper: name of conf. incl. year and location
journal paper: name of journal incl. volume, year and pages
book: publisher, potentially editor
all figures and tables must be referenced in the paper
equations:
all mathematical symbols must be explained
symbols should be used consistently and unambiguously
abbreviations (STFT, DFT, etc.) should be introduced
”The short-time Fourier transform (STFT) is given by (. . .)
We compute the STFT of the signal, (. . .)”

\section{Evaluation}

form (structure, language, form of references)
content (introduction, literature review, algorithm and
evaluation description, figures, comprehensibility, correctness)
evaluation (dataset, metrics, discussion)

\vfill\pagebreak
~
\vfill\pagebreak
